Preregistration analysis, Cost 2 study

### 2019-08-02 Cost2/Cost2_prereg.Rmd
improving survival curve

# Reaction times ECDFs including offer and in-trial quits
(RTs <- dataAll %>%
  #mutate(RT = ifelse(Choice != 0, RT + 2, RT)) %>%
  filter(rawChoice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
  ggplot(aes(RT, color = Cost)) + 
    #stat_ecdf(lwd = 1.2, geom = "smooth") +
    geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
    geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
    scale_color_manual(values = cols) +
    scale_x_continuous(breaks = seq(14)) +
    labs(x = "Time in Trial", y = "Proportion Completed") +
    theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line = element_line(colour = "black"),
      text = element_text(size = 16)))

>>>>

# # Reaction times ECDFs including offer and in-trial quits
# (RTs <- dataAll %>%
#   #mutate(RT = ifelse(Choice != 0, RT + 2, RT)) %>%
#   filter(rawChoice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
#   ggplot(aes(RT, color = Cost)) + 
#     #stat_ecdf(lwd = 1.2, geom = "smooth") +
#     geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
#     geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
#     scale_color_manual(values = cols) +
#     scale_x_continuous(breaks = seq(14)) +
#     labs(x = "Time in Trial", y = "Proportion Completed") +
#     theme(panel.grid.major = element_blank(),
#       panel.grid.minor = element_blank(),
#       panel.background = element_blank(),
#       axis.line = element_line(colour = "black"),
#       text = element_text(size = 16)))

# NEW VERSION OF SURVIVAL. BUT STILL NEEDS A BIT OF WORK. ALSO, CHECK THAT RT > 14s

library(survival)
library(ggfortify)

# this version of a survival curve forces all successful acceptances to have an RT of 14
# that's to avoid jumps from 2s to 10s to 14s
# 1 - Choice is to reverse the coding of choices, since the survival package assumes 0 = censor?
temp <- dataAll %>%
    filter(rawChoice < 2) %>% 
    mutate(#RT = ifelse(Choice == 1, 14, RT),
           Choice = 1 - Choice)

survData <- survfit(Surv(RT, Choice) ~ Cost, data = temp)

autoplot(survData) +
  geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  scale_x_continuous(breaks = seq(14)) +
  ylim(0, 1) +
  labs(x = "Time in Trial", y = "Proportion Completed") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        text = element_text(size = 16))
